Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-10-22 Methods-and-Results.Rmd
simple ML contact test adapted

\paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}”. Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts. These participants are removed from any analyses that focus on outgroup contacts.}.

@@

\subsubsection{Contact Hypothesis}
<!-- We tested the most general contact hypothesis in two steps. First, we assessed whether overall between participants more intergroup interactions were related to to more positive average outgroup attitudes. Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions). We find that neither the overall number of contacts nor the number of experience sampling responses with a contact were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`). However, we did find a medium sized correlation between the participants' average contact quality and their average outgroup attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`). And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).  -->
We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance. This is unusual and might indicate that the effect is very consistent across participants. However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}. 
Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data. While this offers support for the most basic premise of the intergroup contact hypothesis (i.e., that any interaction will lead to more positive outgroup attitudes), this analysis does not consider any notion of interaction quality. We assess the conditional effects of interaction numbers and interaction quality ratings after we report on the individual studies to avoid under-powered analyses.

@@

\paragraph{Intergroup Contact}To measure intergroup contacts, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (in-person interaction for at least 10 minutes)}”. Participants were additionally offered a pop-up explanation: "With in-person interaction, we mean a continued interaction with another person (potentially in a group) that lasted at least 10 minutes. This interaction should be offline and face-to-face. It should include some form of verbal communication and should be uninterrupted to still count as the same interaction. Any individual interaction can last minutes or hours. If there were multiple interaction partners, we would like you to focus on the person that was most important to you during the interaction.". The participants recorded between `r dtStudentSupp$studentContactFreq$SumContactNL[dtStudentSupp$studentContactFreq$SumContactNL > 0] %>% min`--`r dtStudentSupp$studentContactFreq$SumContactNL %>% max`
interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtStudentSupp$studentContactFreq$SumContactNL) / nrow(dtStudentSupp$studentInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtStudentSupp$studentInteractionType), big.mark=",")` experience sampling responses).

@@

# Save variances
mdlStudent$varAttNull <- 
  VarCorr(mdlStudent$lmeAttNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlStudent$tauAttNull <- 
  as.numeric(mdlStudent$varAttNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlStudent$sigmaAttNull <- 
  as.numeric(mdlStudent$varAttNull[2])
# The ICC estimate (between/between+within) is:
mdlStudent$IccAttNull <-
  (as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))
mdlStudent$IccPercAttNull <-
  ((as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))) * 100
```
```{r studentModelInterceptAttType, include = FALSE}
# Create and save Model
mdlStudent$lmeInterceptAttType <-
  lme(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
    random =  ~ 1 | PID,
    data = dtStudentSupp$studentInteractionType
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlStudent$lmerInterceptAttType <- lmer(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
    data = dtStudentSupp$studentInteractionType
  ),
  confint = TRUE,
  digits = 3
)

@@

# Save variances
mdlStudent$varInterceptAttType <- 
  lme4::VarCorr(mdlStudent$lmeInterceptAttType)
```
```{r studentModelSlopesInteractionType, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlStudent$lmeSlopesAttType <- lme(
  AttitudesDutch ~
    OutgroupInteraction + NonOutgroupInteraction,
  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
  control = lmeControl(opt = "optim"),
  data = dtStudentSupp$studentInteractionType
)

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlStudent$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteraction + NonOutgroupInteraction +
      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
    data = dtStudentSupp$studentInteractionType
  ), 
  confint = TRUE,
  digits = 3
)

@@

\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis as in Study 1. We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). However, we found no significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong} and Figure \ref{fig:ContactHypothesis}). We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, as well as Online Supplementary Material A). Thus, in our second data set we find mixed results; outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants. However, we find that this effect does not depend on the average perceived interaction quality. This unexpected results, might be due to the aggregation process and the following analyses will focus in on the role of the perceived interaction quality during an outgroup interaction.

@@

\paragraph{Intergroup Contact}The measurement of intergroup contacts was identical to Study 2. The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtMedical$full), big.mark=",")` experience sampling responses).

@@

```{r medicalModelInterceptAttType, include = FALSE}
# Create and save Model
mdlMedical$lmeInterceptAttType <-
  lme(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
    random =  ~ 1 | PID,
    na.action=na.omit,
    data = dtMedical$full
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedical$lmerInterceptAttType <- lmer(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
    data = dtMedical$full
  ),
  confint = TRUE,
  digits = 3
)

@@

```{r medicalModelSlopesInteractionType, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedical$lmeSlopesAttType <- lme(
  AttitudesDutch ~
    OutgroupInteraction + NonOutgroupInteraction,
  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
  control = lmeControl(opt = "optim"),
  na.action = na.omit,
  data = dtMedical$full
)

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedical$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteraction + NonOutgroupInteraction +
      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
    data = dtMedical$full
  ), 
  confint = TRUE,
  digits = 3
)

>>>>

\paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}”. Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtWorkerSupp$workerAvFreQual$SumContactNL), big.mark=",")` of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts. These participants are removed from any analyses that focus on outgroup contacts.}.

@@

\subsubsection{Contact Hypothesis}
<!-- We tested the most general contact hypothesis in two steps. First, we assessed whether overall between participants more intergroup interactions were related to to more positive average outgroup attitudes. Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions). We find that neither the overall number of contacts nor the number of experience sampling responses with a contact were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`). However, we did find a medium sized correlation between the participants' average contact quality and their average outgroup attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`). And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).  -->
We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently). Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors. Nonetheless, we also offer an analysis of the joint data sets in Online Supplemental Material A (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance. This is unusual and might indicate that the effect is very consistent across participants. However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}. 
Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data. While this offers support for the most basic premise of the intergroup contact hypothesis (i.e., that any interaction will lead to more positive outgroup attitudes), this analysis does not consider any notion of interaction quality. We assess the conditional effects of interaction numbers and interaction quality ratings after we report on the individual studies to avoid under-powered analyses.

@@

\paragraph{Intergroup Contact}To measure intergroup contacts, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (in-person interaction for at least 10 minutes)}”. Participants were additionally offered a pop-up explanation: "With in-person interaction, we mean a continued interaction with another person (potentially in a group) that lasted at least 10 minutes. This interaction should be offline and face-to-face. It should include some form of verbal communication and should be uninterrupted to still count as the same interaction. Any individual interaction can last minutes or hours. If there were multiple interaction partners, we would like you to focus on the person that was most important to you during the interaction.". The participants recorded between `r dtStudentSupp$studentContactFreq$SumContactNL[dtStudentSupp$studentContactFreq$SumContactNL > 0] %>% min`--`r dtStudentSupp$studentContactFreq$SumContactNL %>% max`
interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtStudentSupp$studentContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtStudentSupp$studentInteractionType), big.mark=",")` experience sampling responses).

@@

# Save variances
mdlStudent$varAttNull <- 
  VarCorr(mdlStudent$lmeAttNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlStudent$tauAttNull <- 
  as.numeric(mdlStudent$varAttNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlStudent$sigmaAttNull <- 
  as.numeric(mdlStudent$varAttNull[2])
# The ICC estimate (between/between+within) is:
mdlStudent$IccAttNull <-
  (as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))
mdlStudent$IccPercAttNull <-
  ((as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))) * 100
```
```{r studentModelInterceptAttType, include = FALSE}
# Create and save Model
mdlStudent$lmeInterceptAttType <-
  lme(
    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
    random =  ~ 1 | PID,
    data = dtStudentSupp$studentInteractionType
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlStudent$lmerInterceptAttType <- lmer(
    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
    data = dtStudentSupp$studentInteractionType
  ),
  confint = TRUE,
  digits = 3
)

@@

# Save variances
mdlStudent$varInterceptAttType <- 
  lme4::VarCorr(mdlStudent$lmeInterceptAttType)
```
```{r studentModelSlopesInteractionType, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlStudent$lmeSlopesAttType <- lme(
  AttitudesDutch ~
    OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
  random = ~ 1 + OutgroupInteractionC + NonOutgroupInteractionC | PID,
  control = lmeControl(opt = "optim"),
  data = dtStudentSupp$studentInteractionType
)

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlStudent$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
    data = dtStudentSupp$studentInteractionType
  ), 
  confint = TRUE,
  digits = 3
)

@@

\subsubsection{Contact Hypothesis}
<!-- We tested the most general contact hypothesis as in Study 1. We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). However, we found no significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong} and Figure \ref{fig:ContactHypothesis}).  -->
We tested the most general contact hypothesis as we did for Study 1. We, again, used a multilevel regression analysis to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently). We again added the participant means back into the model. Because these are the means of the contact dummy variables they are the proportion of measurements that included a particular contact. This not only adjusts the model for unequal cell sizes but allows us to see whether between subject differences in the relative number of interactions had an effect on outgroup attitudes. We find that in this data set participant-level outgroup contact proportions were also a positive predictor of outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionM")`). The relative number of non-outgroup interactions showed no such effect (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, as well as Online Supplementary Material A). 
Thus, in our second data set we find that outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.

@@

\paragraph{Intergroup Contact}The measurement of intergroup contacts was identical to Study 2. The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtMedicalSupp$medicalContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtMedical$full), big.mark=",")` experience sampling responses).

@@

```{r medicalModelInterceptAttType, include = FALSE}
# Create and save Model
mdlMedical$lmeInterceptAttType <-
  lme(
    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
    random =  ~ 1 | PID,
    na.action=na.omit,
    data = dtMedical$full
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedical$lmerInterceptAttType <- lmer(
    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
    data = dtMedical$full
  ),
  confint = TRUE,
  digits = 3
)

@@

```{r medicalModelSlopesInteractionType, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlMedical$lmeSlopesAttType <- lme(
  AttitudesDutch ~
    OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
  random = ~ 1 + OutgroupInteractionC + NonOutgroupInteractionC | PID,
  control = lmeControl(opt = "optim"),
  na.action = na.omit,
  data = dtMedical$full
)

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedical$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
    data = dtMedical$full
  ), 
  confint = TRUE,
  digits = 3
)
